Fluid structure interaction with ETVF

### 2021-11-19 manuscript/paper.tex
Fresh code to work with. 6 simulations in total.

\subsection{Discrete governing equations}

In this current paper the fluid medium is modelled using the improvised scheme
of TVF, which is been applied to the free surface flows, called ETVF.

For detailed derivation we point the reader to paper \cite{cite our paper},
here we only give the discrete equations.

@@

\begin{multline}
  \label{eq:sph-discretization-edac}
  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; - \;
  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
  4 \; \nu_{edac}
  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + EPS)} \ten{r}_{ab}
  \bigg) \; \cdot \nabla_{a} W_{ab}
\end{multline}

\begin{multline}
  \label{eq:sph-momentum-fluid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}\bigg) \bigg]
  \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot \nabla_{a} W_{ab} +
  \ten{g}_{a}.
\end{multline}

\begin{equation}
  \label{eq:sph-momentum-solid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2}\bigg) \bigg]  \nabla_{a} W_{ab} +
  \ten{g}_{a}.
\end{equation}

@@

In both fluid and solid modelling, the pressure is computed using an
isothermal equation of state, given as,
\begin{equation}
  \label{eq:pressure-equation}
  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
\end{equation}
where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
$\rho_0$ are the reference speed of sound and density, respectively.

@@

>>>>

\subsection{Solid mechanics equations}

@@

\begin{equation}
  \label{eq:sph-momentum-solid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2} + \Pi_{ab} \ten{I} \bigg) \bigg]  \cdot \nabla_{a} W_{ab} +
  \ten{g}_{a},
\end{equation}

$\Pi_{ab}$ is the artificial
viscosity~\cite{monaghan-review:2005} to maintain the stability of the
numerical scheme. It is given as,
\begin{align}
  \label{eq:mom-av}
  \Pi_{ab} =
  \begin{cases}
\frac{-\alpha h_{ab} \bar{c}_{ab} \phi_{ab}}{\bar{\rho}_{ab}}
  & \ten{u}_{ab}\cdot \ten{r}_{ab} < 0, \\
  0 & \ten{u}_{ab}\cdot \ten{r}_{ab} \ge 0,
\end{cases}
\end{align}
where,
%
\begin{equation}
  \label{eq:av-phiij}
  \phi_{ab} = \frac{\ten{u}_{ab} \cdot \ten{r}_{ab}}{r^2_{ab} + 0.01 h^2_{ab}},
\end{equation}
%
where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
viscosity parameter.

@@

\begin{equation}
  \label{eq:pressure-equation}
  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
\end{equation}
where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
$\rho_0$ are the reference speed of sound and density, respectively.

@@

\begin{table}[!ht]
  \centering
  \begin{tabular}[!ht]{ll}
    % \toprule
    Quantity & Values \\
    % \midrule
    $D$, Diameter & 2m \\
    $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
    $c_s$ & 10m/s \\
    $D/\Delta x_{\max}$, lowest resolution & 4 \\
    $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
    $C_r$ & 1.08 \\
    Reynolds number & 40, 550, 1000, 3000, and 9500 \\
    Time of simulation & 6 \\
    % \bottomrule
  \end{tabular}
  \caption{Parameters used for the flow past a circular cylinder problem.}%
  \label{tab:fpc-params}
\end{table}
